%%% Template originaly created by Karol Kozioł (mail@karol-koziol.net) and modified for ShareLaTeX use

\documentclass[a4paper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{xcolor}

\renewcommand\familydefault{\sfdefault}
\usepackage{tgheros}
\IfFileExists{droidsansmono.sty}{\usepackage[defaultmono]{droidsansmono}}{\usepackage[defaultmono]{droidmono}}

\usepackage{amsmath,amssymb,amsthm,textcomp}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{geometry}
\geometry{left=25mm,right=25mm,%
bindingoffset=0mm, top=20mm,bottom=20mm}


\linespread{1.3}

\newcommand{\linia}{\rule{\linewidth}{0.5pt}}

% custom theorems if needed
\newtheoremstyle{mytheor}
    {1ex}{1ex}{\normalfont}{0pt}{\scshape}{.}{1ex}
    {{\thmname{#1 }}{\thmnumber{#2}}{\thmnote{ (#3)}}}

\theoremstyle{mytheor}
\newtheorem{defi}{Definition}

% my own titles
\makeatletter
\renewcommand{\maketitle}{
\begin{center}
\vspace{2ex}
{\huge \textsc{\@title}}
\vspace{1ex}
\\
\linia\\
\@author \hfill \@date
\vspace{4ex}
\end{center}
}
\makeatother
%%%

% custom footers and headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{Assignment: PageRank Paper Review}
\cfoot{}
\rfoot{Page \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%

% multicol tables
\usepackage{colortbl}
\usepackage{enumitem}
\newlist{tabitemize}{itemize}{1}
\setlist[tabitemize]{label=\textbullet,nosep,after=\strut,align=parleft,leftmargin=*,}

\usepackage{calc}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1\textwidth-2\tabcolsep-0.6pt}}

% code listing settings
\usepackage{listings}
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    aboveskip={1.0\baselineskip},
    belowskip={1.0\baselineskip},
    columns=fixed,
    extendedchars=true,
    breaklines=true,
    tabsize=4,
    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
    frame=lines,
    showtabs=false,
    showspaces=false,
    showstringspaces=false,
    keywordstyle=\color[rgb]{0.627,0.126,0.941},
    commentstyle=\color[rgb]{0.133,0.545,0.133},
    stringstyle=\color[rgb]{01,0,0},
    numbers=left,
    numberstyle=\small,
    stepnumber=1,
    numbersep=10pt,
    captionpos=t,
    escapeinside={\%*}{*)}
}

%%%----------%%%----------%%%----------%%%----------%%%

\begin{document}

\title{Assignment: PageRank Paper Review}

\author{William Panlener, University of Mississippi}

\date{04/28/2020}

\maketitle

\section*{Paper Reviewed}

[6] Taher Haveliwala. Efficient computation of pagerank.  Technical report, Stanford University, 1999.

\section*{Summary of Authors Contributions}

The author sought to improve the efficiency of PageRank. He proposed three solutions: (1) blocking of data structures to reduce disk overhead in memory constrained systems, (2) use of single-precision weights, and (3) early termination of PageRank iterations.

(1) To avoid expensive hard disk seeks during PageRank iterations, the author blocked data structures needed to compute weights for a subgraph such that the weight calculation relied on no data outside of the block. These blocks were chosen so that they would approach but not exceed total memory size so as to not cause disk swapping while also keeping the context switching between blocks low. In a situation where memory size was significantly less than the data structures required to calculate weights, this approach showed approximately a 1000x speedup over the naive approach of randomly accessing the data structures.

(2) The author determined that PageRank weights could be represented in single-precision rather than double-precision, causing the algorithm to require significantly less memory. The author tested this by computing weights over 100 iterations in two batches. Batch A represented the weights as single-precision and Batch B represented the weights as double-precision. The author noted insignificant residuals between the batches.

(3) The author observed that terminating PageRank iterations after between iterations dropped below a threshhold may be causing the algorithm to perform an unnecessary number of iterations. A truer benchmark for when sufficient iterations have occurred is when the order of nodes holding the highest weight no longer changes frequently. He determined through weight calculation and an analysis of ranking stability that this iteration threshhold may be an order of magnitude lower than what is expected when treshholding between-iteration residuals.

\section*{Critique}

The author proposed a vision of using these efficiency improvements to enable decentralized (read on the user's device) computation of personalized PageRank weights. He proposed that the user would receive frequent updates of the link graph structure of the Internet on a cd-rom and would periodically dedicate all resources of the computer for more than 100 minutes to recomputing personalized PageRank weights using bookmarks and browsing history as priority destinations for random jumps. I was confused that this decentralized vision was proposed only one year after the original Brin/Page PageRank paper by a student from the same lab when Brin/Page had presented a pretty clear vision of centralized indexing.

I think an improvement to the paper would have been to either omit the decentralized vision or present the PageRank improvements as a means to reduce the cost of nodes in a centralized indexing system or to reduce the amount of work required by such nodes.

I also disliked that the author made the determination that single-precision weights were sufficient by comparing residuals between 100-iteration runs of single-precision vs double-precision weight computation. The distaste for this evaluation stemmed from the author in his third contribution encouraging an order of magnitude fewer iterations. I think the paper would benefit from re-evaluating the second contribution in terms of either residual or rank order analysis with this lower number of iterations.

\end{document}
